\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-03-05 doc/USER_MANUAL/05_running_the_solver.tex
updates reading Par_file location for simultaneous runs (single file, should be in ./DATA/, not in run**/DATA/)

We have also added the ability to run several calculations (several earthquakes)
in an embarrassingly-parallel fashion from within the same run;
this can be useful when using a very large supercomputer to compute
many earthquakes in a catalog, in which case it can be better from
a batch job submission point of view to start fewer and much larger jobs,
each of them computing several earthquakes in parallel.
To turn that option on, set parameter \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}
to a value greater than 1 in file setup/constants.h.in before
configuring and compiling the code.
When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS},
all the individual runs must use the same number of processor cores,
which as usual is \texttt{NPROC} in the input file \texttt{DATA/Par\_file},
and thus the total number of processor cores to request from the batch system
should be \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS $\times$ NPROC}.
All the runs to perform must be placed in directories called \texttt{run0001}, \texttt{run0002}, \texttt{run0003} and so on (with exactly four digits)
and you must create a link from the root directory of the code
to the first copy of the executable programs by typing \texttt{ln -s run0001/bin bin}.

>>>>

\section{Note on the simultaneous simulation of several earthquakes}

We have also added the ability to run several calculations (several earthquakes)
in an embarrassingly-parallel fashion from within the same run;
this can be useful when using a very large supercomputer to compute
many earthquakes in a catalog, in which case it can be better from
a batch job submission point of view to start fewer and much larger jobs,
each of them computing several earthquakes in parallel.
To turn that option on, set parameter \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS}
to a value greater than 1 in file \texttt{DATA/Par\_file}.

When that option is on, of course the number of processor cores used to start
the code in the batch system must be a multiple of \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS},
all the individual runs must use the same number of processor cores,
which as usual is \texttt{NPROC} in the input file \texttt{DATA/Par\_file},
and thus the total number of processor cores to request from the batch system
should be \texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS $\times$ NPROC}.

\begin{figure}[H]
\begin{centering}
\includegraphics[width=2.2in]{figures/simultaneous_dir_struct.pdf}
\par\end{centering}
%
\caption{
Directory structure when simulating several earthquakes at once.
To improve readability, only directories have been drawn.}
\label{fig:simultaneous_dir_struct}
\end{figure}

Figure~\ref{fig:simultaneous_dir_struct} shows what the directory structure
should looks like when simulating multiple earthquakes at ones.
All the runs to perform must be placed in directories called \texttt{run0001}, \texttt{run0002}, \texttt{run0003} and so on (with exactly four digits).

\begin{itemize}
\item The simulation is launched within the root directory \texttt{EXAMPLE\_ROOT\_DIR}\\
(usually \texttt{mpirun -np N ./bin/xspecfem3D}).
\item \texttt{DATA} should contain the \texttt{Par\_file} parameter file with
\texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS} as explained in Chapter~\ref{cha:Creating-Distributed-Databases}.
\item \texttt{DATABASES\_MPI} and {OUTPUT\_FILES} directory may contain the mesher output but they
are not required as they are superseded by the ones in the \texttt{runXXX} directories.
\item \texttt{runXXXX} directories must be created beforehand. There should be be as many as
\texttt{NUMBER\_OF\_SIMULTANEOUS\_RUNS} and the numbering should be contiguous, starting from \texttt{0001}.
They all should have \texttt{DATA},
\texttt{DATABASES\_MPI} and \texttt{OUTPUT\_FILES} directories. Additionally a \texttt{SEM} directory
containing adjoint sources have to be created to perform adjoint simulations.
\item \texttt{runXXXX/DATA} directories must all contain a \texttt{CMTSOLUTION} file,
a \texttt{STATIONS} file along with an eventual \texttt{STATIONS\_ADJOINT} file.
\item If \texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL} is set to \texttt{.true.} in \texttt{DATA/Par\_file},
only \texttt{run0001/OUTPUT\_FILES} and \texttt{run0001/DATABASES\_MPI} directories need to contain the files
outputted by the mesher.
\item If \texttt{BROADCAST\_SAME\_MESH\_AND\_MODEL} is set to \texttt{.false.} in \texttt{DATA/Par\_file},
every \texttt{runXXXX/OUTPUT\_FILES} and \texttt{runXXXX/DATABASES\_MPI} directories need to contain the files
outputted by the mesher. Note that while the meshes might have been created from different models and
parameter sets, they should have been created using the same number of MPI processes.
\end{itemize}
